\section{Motivation}

% TLP is a great tool for esd analysis
Throughout this document, and in the \gls{esd} field, the \gls{tlp} generator is used extensively as a characterization and testing tool.
Amoung its many advantages, it generates very clean and controllable pulses in a shielded environment.
It has proven to be a tool of choice for studying, among other things, the behavior of silicon-level devices.

% But ESD gun is required.
Ultimately, \gls{esd-gun} testing is a mandatory requirement to pass most customers' products specifications.
\gls{tlp} testing alone is not a sufficient proof for customers that the integrated circuit can withstand the harsh real environment, especially for automotive applications.
Several standards exist, targeting qualification of devices against electro-static discharges.
The HMM specification(TODO: ref), the IEC 61000-4-2 standard \cite{iec61000-4-2} and the ISO 10605 standard \cite{iso10605} define the same \gls{esd} testing waveform, with different application conditions.

% ESD gun is #1
The common waveform defined as part of those standards is virtually the most widely used stress pulse in ESD testing and ESD qualification of products.
Together, they cover a very large amount of devices from equipment, boards, and integrated circuit, in automotive and consumer.

% Main problems with Gun
By design, the \gls{esd-gun} has certain requirements to make the generated \gls{esd} discharge fit well with real-world conditions.
Incidentally, those requirements make investigation harder because they make injected waveform and setup less reproducible.
For instance, injection is performed through a metallic tip of a few centimeters long.
It reproduces what happens when a human body discharges into an electrical device.
However, the metallic tip radiates heavily during the discharge and up to several gigahertz (TODO: reference).
The ground return on the ESD gun is a large ribbon wire of a few meters long.
This is close to the kind of equivalent ground connection a human body has to the ground.
However, it is also very inductive, and its value can change considerably depending on the shape.
Finally, for integrated circuits in particular, the ESD gun waveform is a lot more complex than the rectangular TLP shape.

% Correlation between TLP and Gun
Unlike the ESD gun, \gls{tlp} generators are extremely well controlled.
The discharge propagates entirely inside coaxial cables and does not generate any \gls{rf} radiation.
In some few cases, failures can be correlated between \gls{TLP} and \gls{esd-gun} (TODO: REF).
However, there is generally no clear link between failures induced by each generator (TODO REF 5).
The lack of correlation is proven further in (TODO REF 4), with 2k\textOmega{} ESD gun discharge modules.
(TODO REF 5) demonstrates that some ESD structures in analog high-voltage technology have completely uncorrelated failure levels between TLP and HMM. Failure analysis shows that the failure mechanisms are different.

% Motivation
The point here is that \gls{TLP} cannot be used as-is to replace ESD gun for qualification.
However, a compromise can be found by modifying a TLP generator to produce the ESD gun waveform, but in a shielded, well-controlled, and reproducible environment.
This approach has been explored in the past by E. Grund [6] and Y. Cao [7].

% Cite previous work on the topic
In (TODO REF 6), a TLP generator is modified by placing an impedance mismatch (resistor) between two coaxial lines.
On the other side, in (TODO REF 7), a capacitive discharge through a short coaxial cable is employed to generate an HMM-compliant pulse.

%TODO Figure Grund alternative

%TODO Figure Cao alternative

%TODO Review next
%TODO What does this new setup brings to the table
The setup described here is a different alternative
Based on propation delays to shape the pulse [ref to me ?].
The ultimate goal is to have a drop-in replacement for ESD guns when investigation is required.

%TODO: Speak about disturbances caused by radiated emissions that cannot be reproduced with a shielded generator
