\section{Study of a real product}
\label{sec:study-real-product}

% The studied product is an analog regulation function from automotive world
This chapter details a study case of a real \gls{asic} from the automotive field exposed to \gls{esd} during its normal operation.
The studied chip performs high-level functions with a few of them rather critical for the car vehicle.
Tests and analysis are focused on one function in particular, the primary voltage regulation function of the device.
In the final application, it is powered directly by the car's battery, and starts the entire product.
It is also a good opportunity to study the behavior of a complex analog function exposed to electrostatic discharges.
This product was designed at NXP, and complete access to the schematic and layout was made available for this research work.
The product operation, architecture and application are described in section \ref{sec:product-desc}.

% The chip is used in a lighter configuration where a failure could be identified
This chip has a recommended application circuit provided by NXP, and a specification.
They define many requirements to ensure proper operation, such as supply voltage range, current capability, etc.
Among all those requirements is also defined the minimum constraints for external capacitive decoupling and filtering.
Those constraints are not required by the functionality itself, but are needed to ensure good performance against electrical stresses with some decent margin.
In this research study, the amount of external decoupling and filtering has been reduced intentionally.
The objective is to reduce the bill of materials of the complete application and thus to diminish the cost for the equipment manufacturer.
With this lighter configuration, and by running \gls{esd} simulations, it has been possible to discover a functional weakness.
The failure is described in detailed in section \ref{sec:failure-case-study}.

\input{src/3/sections/case-study-product.tex}
\input{src/3/sections/s1-functional-fail.tex}
